---
title: "Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(eyelinkReader)
```

The main function is `read_edf()` that imports an EDF file (or throws an error, if EDF API is not installed). By default it will import all events and attempt to extract standard events: saccades, blinks, fixations, logged variables, etc.
```r
library(eyelinkReader)
gaze <- read_edf('eyelink-recording.edf')
```

Events and individual event types are stored as tables inside the `eyelinkRecording` object with `trial` column identifying individual trials. Trial 0 correspond to events (e.g, `DISPLAY_COORDS` message, etc.) sent to the eye tracker before the first trial. 
```r
View(gaze$saccades)
```

The package also includes functions to parse non-standard events: recorded areas of interest (`extract_AOIs`) and trigger events that help to time events (`extract_triggers`). These need to be called separately.

```r
gaze <- extract_AOIs(gaze)
gaze <- extract_triggers(gaze)
```

To import samples, add `import_samples = TRUE` and, optionally, specify which sample attributes need to be imported, e.g., `sample_attributes = c('time', 'gx', 'gy')`. All attributes are imported if `sample_attributes` is not specified. See package and EDF API documentation for the full list of attribute names.

```r
# import samples with all attributes
gaze <- read_edf('eyelink-recording.edf', import_samples = TRUE)

# import samples with selected attributes
gaze <- read_edf('eyelink-recording.edf',
                 import_samples = TRUE,
                 sample_attributes = c('time', 'gx', 'gy'))
```

Please refer to documentation on `eyelinkRecording` class for details on events and samples.
